### 2020-03-09 Common/chapters/abstract.tex
Julien and Johan: proofread until deep learning (included)

% !TEX root = ../main.tex
Automating the detection of cancer participates to an an early detection and treatment, which increases the chances of recovery. Recent algorithms in artificial intelligence relying on deep learning have shown promising results in this field. Indeed, the usefulness of convolutional neural networks (CNNs) for segmentation or classification tasks is no longer to be proven. However, the performance of these models is often limited by the amount of available data to train the algorithm.

This thesis first presents a state-of-the-art convolutional neural network for pro\-state lesion classification. All steps from the data processing to the smallest details regarding the neural network training are explained, ensuring a complete reproducibility of the experiment. This model was evaluated on the official SPIE-AAPM-NCI Prostate MR Classification Challenge dataset and achieved an AUC of 0.76. This result constitutes a solid baseline and confirms the correct functioning of the implementation.

On top of this implementation, a new transfer learning approach using lesions of multiple body parts (brain and lung) was built. This method shows that integrating information from diverse datasets improves automated prostate cancer diagnosis. Indeed, it appears that lesions of these different types of cancer share low-level features that can be used to increase the generalization ability and performance of the prostate lesion classifier. This technique provides a concrete solution to the lack of available data for prostate classification and suggests that many other types of cancers can take advantage of it.

>>>>

% !TEX root = ../main.tex
Automating the detection of cancer participates to an early detection and treatment, which increases the chances of recovery. Recent algorithms in artificial intelligence relying on deep learning have shown promising results in this field. Indeed, the usefulness of convolutional neural networks (CNNs) for segmentation or classification tasks is no longer to be proven. However, the performance of these models is often limited by the amount of data which is available to train the algorithm.

This thesis first presents a state-of-the-art convolutional neural network for pro\-state lesion classification. All steps from the data processing to the smallest detail regarding the neural network training are explained, ensuring a complete reproducibility of the experiment. This model is then evaluated on the official SPIE-AAPM-NCI Prostate MR Classification Challenge dataset, achieving an AUC of 0.76. This result constitutes a solid baseline and confirms the proper functioning of the implementation.

On top of this implementation, a new transfer learning approach using lesions of multiple body parts (brain and lung) is built. This method shows that integrating information from diverse datasets improves automated prostate cancer diagnosis. Indeed, it appears that cancerous lesions coming from various body parts share low-level features that can be used to increase the generalization ability and performance of the prostate lesion classifier. This technique provides a concrete solution to the lack of available data for prostate classification and suggests that many other types of cancer can be taken advantage of. Thanks to this technique, the AUC achieved on our test set increases by 18\% (from 0.68 to 0.80).

### 2020-03-09 Common/chapters/acknowledgements.tex
Johan and Julien: Authors on a new line + authors in abstract hardcoded + indent everywhere and surname everywhere until section deep learning
Julien and Johan: proofread until deep learning (included)

\textbf{Common acknowledgements:}\\
First of all, we would like to thank Dr. Giuseppe Cuccu for his valuable advices, the exciting discussions we had with him and the precious time he took to supervise the project. Even we were struggling to find the cause of bad results for weeks, he always encouraged us and pushed us to give our best. We are extremely grateful to him for his support. We would also like to greatly thank Akansha Bhardwaj for her supervision throughout the project and the amazing work she did reviewing the thesis. Last but not least, we would like to express sincere thanks to Prof. Dr. Philippe Cudré-Mauroux for supervising the project. Having the opportunity to work with such a wonderful team and having access to amazingly powerful machines was incredible.\\

\noindent \textbf{Julien Clément's acknowledgements:}\\
XXX\\

\noindent \textbf{Johan Jobin's acknowledgements:}\\
On a personal note, I would like to acknowledge with gratitude the support of my family, specially my parents (Jean-Bernard and Marie Jobin), my brother (Lucas Jobin), my uncle (Xavier Marchand) and my girlfriend (Julie Timmermans). They have allowed me to be in the best conditions to carry out this work and have expressed great interest in it, which gave me even more motivation. A special thanks goes to my close friends that have always encouraged me. Finally, I would like to thank Julien Clément for the great work we did together on this thesis but also for all the years we have spent at the university. The realization of this work would not have been possible without him.

>>>>

\textbf{Common acknowledgements}\\
First of all, we would like to thank Dr. Giuseppe Cuccu for his valuable advices, the exciting discussions we had and the precious time he took to supervise the project. Even we were struggling to find the cause of disappointing results for weeks, he always encouraged us and pushed us to give our best. We are extremely grateful to him for his support. We would also like to greatly thank Akansha Bhardwaj for her supervision throughout the project and the amazing work she did reviewing the thesis. Last but not least, we would like to express sincere thanks to Prof. Dr. Philippe Cudré-Mauroux for supervising the project. Having the opportunity to work with such a wonderful team and having access to amazingly powerful machines was awesome.\\

\noindent \textbf{Julien Clément's acknowledgements}\\
I wish to thank my close friends and relatives who supported me throughout this work and understood the time-consuming nature of it.

\noindent Also, I’m sincerely grateful for having had the opportunity to work with Johan Jobin. His work ethic and determination to reach new goals despite the obstacles made the completion of this work possible. His kind and wise words were really valuable during tougher times.

\noindent Finally, a special thought goes to my father Joseph who encouraged me to strive for the best throughout his whole life. Having him in mind gave meaning to this cancer-related project and allowed me to keep pushing when needed.\\

\noindent \textbf{Johan Jobin's acknowledgements}\\
On a personal note, I would like to acknowledge with gratitude the support of my family, specially my parents (Jean-Bernard and Marie Jobin), my brother (Lucas Jobin), my uncle (Xavier Marchand) and my girlfriend (Julie Timmermans). They have allowed me to be in the best conditions to carry out this work and have expressed great interest in it, which gave me even more motivation. A special thanks goes to my close friends that have always encouraged me. Finally, I would like to thank Julien Clément for the great work we did together on this thesis but also for all the years we have spent at the university. The realization of this work would not have been possible without him.
